
---
title: "Plotly Demo"
author: "Jacob Robinson"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load required libraries
library(plotly)
library(dplyr)
library(ggplot2)
```

## Introduction

This presentation demonstrates interactive data visualization using Plotly in R.

## Sample Data Analysis

Let's analyze some sample data:

```{r data-prep}
# Create sample dataset
set.seed(123)
sample_data <- data.frame(
  category = rep(c("A", "B", "C", "D"), each = 25),
  value = c(rnorm(25, 10, 2), rnorm(25, 15, 3), rnorm(25, 12, 2.5), rnorm(25, 8, 1.5)),
  time = rep(1:25, 4)
)

# Preview the data
head(sample_data)
```

## Interactive Scatter Plot

```{r plotly-chart}
# Create interactive scatter plot
p <- sample_data %>%
  plot_ly(
    x = ~time, 
    y = ~value, 
    color = ~category,
    type = 'scatter', 
    mode = 'markers',
    marker = list(size = 10, opacity = 0.7),
    hovertemplate = paste(
      "<b>Category:</b> %{color}<br>",
      "<b>Time:</b> %{x}<br>",
      "<b>Value:</b> %{y:.2f}<br>",
      "<extra></extra>"
    )
  ) %>%
  layout(
    title = "Interactive Scatter Plot by Category",
    xaxis = list(title = "Time"),
    yaxis = list(title = "Value"),
    hovermode = "closest"
  )

p
```

## Box Plot Comparison

```{r box-plot}
# Create interactive box plot
box_plot <- sample_data %>%
  plot_ly(
    y = ~value, 
    x = ~category, 
    type = 'box',
    boxpoints = 'outliers',
    hovertemplate = paste(
      "<b>Category:</b> %{x}<br>",
      "<b>Value:</b> %{y:.2f}<br>",
      "<extra></extra>"
    )
  ) %>%
  layout(
    title = "Distribution Comparison by Category",
    xaxis = list(title = "Category"),
    yaxis = list(title = "Value")
  )

box_plot
```

## Time Series Visualization

```{r time-series}
# Create time series plot
time_series <- sample_data %>%
  plot_ly(
    x = ~time, 
    y = ~value, 
    color = ~category,
    type = 'scatter', 
    mode = 'lines+markers',
    line = list(width = 2),
    marker = list(size = 6)
  ) %>%
  layout(
    title = "Time Series by Category",
    xaxis = list(title = "Time"),
    yaxis = list(title = "Value"),
    hovermode = "x unified"
  )

time_series
```

## Summary

This presentation demonstrated three types of interactive visualizations using Plotly:

- **Scatter Plot**: Shows individual data points with hover information
- **Box Plot**: Compares distributions across categories  
- **Time Series**: Displays trends over time with multiple series

The interactive features allow viewers to hover, zoom, pan, and toggle legend items.